Paper 2014 - A talk about Network

### 2014-08-25 anglais/paper.tex
corrected version of paper

	\begin{itemize}
		\itemsep0em
		\item \textbf{Protocols}:
			specific method used to describe the mechanism, the fields of data, bits, bytes,
			the order of operations and data to send and receive to make a working-communication.

		\item \textbf{Internet Provider}: 
			companies interconnected with other companies which enables you to reach different networks.
			All of these different networks make "the Internet", it's simply a lot of interconnected-networks.

		\item \textbf{Checksum}: 
			a fast operation which consist of make the sum of the data with an algorythm more or less secure.
			This mechanism enables protocol to know if the payload is altered or not by doing the same operation
			and comparing the checksum value. Safer is the checksum, longer and slower it is.

		\item \textbf{Data encapsulation}: 
			the fact of put data on a larger container.

		\item \textbf{Response mechanism}: 
			when you receive data, you can response to it just by fill in the application payload
			with your response, then swaping source and destination address on headers.

		\item \textbf{Subnet}: 
			each IP contained on the same subnets can communicate each other without router, a router
			is the device that enables communication between multiple subnets.

		\item \textbf{TCP}: 
			protocol which enables "secure" connection with a negociation (handshake) before working. It provides
			an acknowledgment and retransmission light but optimized system.

		\item \textbf{UDP}: 
			protocol less "secure" than TCP because it does not support retransmission, acknowledgment and handshake,
			but is very smaller than TCP. This protocol is often used for multimedia content streaming.

		\item \textbf{Switch}: 
			devices that works on layer 2 only and forward frame on the right (destination address) physical port.

		\item \textbf{Router}: 
			interconnect multiple subnet and take decision for routing (best path, etc.)

		\item \textbf{Firewall}: 
			security software which analyze traffic and take decision based on users rules.

>>>>

	\begin{itemize}
		\itemsep0em
		\item \textbf{Protocols}:
			specific methods used to describe the mechanism, the fields of data, bits, bytes,
			the order of operations and data to send and receive to make a working communication.

		\item \textbf{Internet Provider}: 
			companies interconnected with other companies which enable you to reach different networks.
			All of these different networks make "the Internet", it's simply a lot of interconnected networks.

		\item \textbf{Checksum}: 
			a fast operation which consists of making the sum of the data with an algorythm more or less secure.
			This mechanism enables protocols to know if the payload is altered or not by doing the same operation
			and comparing the checksum value. The safer the checksum is, the longer and slower it is.

		\item \textbf{Data encapsulation}: 
			the act of putting data in a larger container.

		\item \textbf{Response mechanism}: 
			when you receive data, you can response to it just by filling in the application payload
			with your response, then swapping the source and the destination addresses on headers.

		\item \textbf{Subnet}: 
			each IP contained on the same subnets can communicate with the others without a router, a router
			is the device that enables communication between multiple subnets.

		\item \textbf{TCP}: 
			protocol which enables a "secure" connection with a negociation (handshake) before working. It provides
			an acknowledgment and retransmission light but with an optimized system.

		\item \textbf{UDP}: 
			protocol less "secure" than TCP because it doesn't support retransmission, acknowledgment and handshake,
			but is much smaller than TCP. This protocol is often used for multimedia content streaming.

		\item \textbf{Switch}: 
			devices that work on layer 2 only and forward frame on the right (destination address) physical port.

		\item \textbf{Router}: 
			interconnects multiple subnets and take decisions for routing (best path, etc.)

		\item \textbf{Firewall}: 
			security software which analyzes traffic and takes decisions based on the user's rules.
